Scalar on Function Regression \\ with Applications to Near-Infrared Spectography

### 2022-01-14 Presentation/slides.tex
Update slides.tex
Slide Update
Slides Update

		\begin{itemize}
			\item The larger $K$, the better fit to the data with also fitting noise
			\item If $K$ is too small, it would miss some significant information
		\end{itemize}
	\end{frame}

	\begin{frame}{Trade Off between Bias and Variance}
		\begin{minipage}[t]{\textwidth}
			\includegraphics[height = 7cm]{../Graphics/Tradeoff.png}
		\end{minipage}
	\end{frame}

@@

	\begin{frame}{FPCA - Plots}
		\begin{minipage}[c]{0.78\textwidth}
			\includegraphics[width = \textwidth]{../Graphics/principal_components.pdf}
			\includegraphics[width = \textwidth]{../Graphics/pc_approx.pdf}
		\end{minipage}
		\begin{minipage}[c]{0.19\textwidth}
			The math is for intuition. In practice there are problems and the fpc's are derived differently.
		\end{minipage}
	\end{frame}

>>>>

		\begin{itemize}
			\item The larger $K$, the better fit to the data, but also more fitting noise
			\item If $K$ is too small, the expansion would miss some significant information
		\end{itemize}
	\end{frame}

	\begin{frame}{Trade Off between Bias and Variance}
		\begin{figure}\notag
			\includegraphics[width = \textwidth]{../Graphics/basis_expansions.pdf}
		\end{figure}
	\end{frame}

@@

	\begin{frame}{FPCA - Plots}
			%\includegraphics[width = \textwidth]{../Graphics/principal_components.pdf}
			\includegraphics[width = \textwidth]{../Graphics/pc_approx.pdf}
	\end{frame}
